---
title: "Developing Data Products Course Project"
author: "Dave Rohrbaugh"
date: "March 11, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Model fitting with polynomials
- Random cubic data was generated using the following code:
```{r data, echo=TRUE}
  q <- seq(from = 0, to = 25, by = 0.1)
  y <- 100 + 0.4 * (q - 10)^3
```
- Noise was added to the y variable:
```{r noise, echo=TRUE}
  noise <- rnorm(length(q), mean = 10, sd = 80)
  ynoise <- y + noise
```
- The data is then fit with a model, where the order of the polynomial (poly_ord) is user selectable.
```{r model, echo=TRUE}
  poly_ord <- 3
  model <- lm(ynoise ~ poly(q, poly_ord, raw = TRUE))
```
## Model Evaluation

- Summary of model given in table.
```{r table, echo=FALSE}
round(summary(model)$coefficients,3)
```
- R Squared valued displayed.
- User can imput a value and a predicted value is returned.

## Example Output Plot
- Ouput plot shows the original data, fit line, confidence intervals, and user selected value to predict (red dot).
```{r plot, echo = FALSE}
    predictor <- 5
    modelpred <- predict(model, newdata = data.frame(q = predictor))
    plot(q, ynoise, col = 'deepskyblue4', xlab = 'index', ylab = "output variable", main = 'Random data')
    predicted.intervals <- predict(model, data.frame(x = q),interval = 'confidence', level=0.95)
    lines(q,predicted.intervals[,1],col = 'green',lwd = 3)
    lines(q,predicted.intervals[,2],col = 'black',lwd = 1)
    lines(q,predicted.intervals[,3],col = 'black',lwd = 1)
    points(predictor, modelpred, col = "red", pch = 16, cex = 2)
    legend("bottomright",
       c("Observ.","Predicted"), 
       col = c("deepskyblue4","green"),
       pch = c(1,NA),
       lty = c(NA,1),
       lwd = c(1,3) )
```

## Shiny App and Code on GitHub
- The Shiny app can be found at:
https://p0rter2000.shinyapps.io/CourseProjectShinyApp/

- The code for ui.R and server.R can be found at:
https://github.com/p0rter2000/DataProductsProject
